An Effective Model of HL-60 Differentiation

### 2017-01-24 Paper_v2.tex
Working thru the results

The signal integration and phenotype modules described ATRA-induced gene expression events in wild-type HL-60 cells (Fig. \ref{fig:model-grn-simulations}).
The signal initiation module produced two outputs, activated Trigger and cRaf-pS621 which drove the expression of ATRA-induced transcription factors,
which then in turn activated the phenotypic program. In particular, Trigger, which is a surrogate for the RAR$\alpha$/RXR transcriptional complex,
regulated the expression of the transcription factors CCATT/enhancer binding protein $\alpha$ (C/EBP$\alpha$), PU.1, and EGR1.
In turn, these transcription factors, in combination with cRaf-pS621, regulated the expression of downstream phenotypic markers such as CD38, CD11b or P47Phox.
We assembled the connectivity of the signal integration and phenotypic programs driven by Trigger and cRaf-pS621 from literature (Table ZZ).
We estimated the parameters which appeared in the control laws regulating these programs
from steady-state and dynamic measurements of transcription factor and phenotypic marker expression following the addition of ATRA [REFHERE].
However, the bulk of the remaining model parameters were taken from directly from literature [REFHERE] and were not estimated from data in this study (see materials and methods).
The model simulations captured the time dependent expression of CD38 and CD11b following the addition ATRA (Fig. \ref{fig:model-grn-simulations}A),
and the steady-state for signal integration and phenotypic markers (Fig. \ref{fig:model-grn-simulations}B).
Taken together, the signal integration and phenotypic simulations were consistent with measurements, thereby validating the assumed molecular connectivity.

>>>>

The signal integration and phenotype modules described ATRA-induced gene expression events in wild-type HL-60 cells (Fig. \ref{fig:model-grn-simulations}).
The signal initiation module produced two outputs, activated Trigger and cRaf-pS621 which drove the expression of ATRA-induced transcription factors,
which then in turn activated the phenotypic program. In particular, Trigger, which is a surrogate for the RAR$\alpha$/RXR transcriptional complex,
regulated the expression of the transcription factors CCATT/enhancer binding protein $\alpha$ (C/EBP$\alpha$), PU.1, and EGR1.
In turn, these transcription factors, in combination with cRaf-pS621, regulated the expression of downstream phenotypic markers such as CD38, CD11b or P47Phox.
We assembled the connectivity of the signal integration and phenotypic programs driven by Trigger and cRaf-pS621 from literature (Table ZZ).
We estimated the parameters which appeared in the control laws regulating these programs
from steady-state and dynamic measurements of transcription factor and phenotypic marker expression following the addition of ATRA [REFHERE].
However, the bulk of the remaining model parameters were taken from directly from literature [REFHERE] and were not estimated in this study (see materials and methods).
The model simulations captured the time dependent expression of CD38 and CD11b following the addition ATRA (Fig. \ref{fig:model-grn-simulations}A),
and the steady-state for signal integration and phenotypic markers (Fig. \ref{fig:model-grn-simulations}B).
Taken together, the signal integration and phenotypic simulations were consistent with measurements, thereby validating the assumed molecular connectivity.
